\vspace{-3em} \includegraphics[width=5cm]{Figures/datarea.pdf} \\ {\large \#SummerDataChallenge}

### 2014-10-01 report/article_4.tex
logo swap

%% additional packages:
\usepackage{wrapfig}
\usepackage[left=1.5in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{caption}

@@

\title{\includegraphics[width=5cm]{Figures/datarea.pdf} \\
{\large \#SummerDataChallenge}} % The article title

@@

I analysed the {\bf London house prices} dataset is several innovative
ways. Firstly \emph{fractal context} shows how house sales within an
arbitrary area relate to those if neighbouring districs, up and down
the postcode hierarchy. Secondly, I employed \emph{ARIMA forecasting}
to extrapolate an area's price trend with an eye to suggesting
profitable investments. Finally, these and other metrics were combined
into an \emph{investment grade} for a given postcode area. Combined
this set of analyses forms the basis of \logo, a product aimed at
``democratising real estate investment'', offering individuals and
businesses quantitative insights for data-driven investment
decisions.

A fully-featured report is online at {\bf \href{http://blm.io/datarea}{blm.io} }and
scripts to reproduce all analyses are available from
{\bf \href{http://github.com/blmoore/summerdatachallenge}{github}}.

@@

When considering a property in a given area, you may ask a realtor
questions like, how do prices here compare to surrounding postcodes?
How have prices increased over time?

\setlength{\intextsep}{.1em}
\begin{wrapfigure}{R}{.45\textwidth}
\begin{center}
\includegraphics[width=.44\textwidth]{Figures/fractal.png}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
\end{center}
\end{wrapfigure}

A real estate professional can give an opinion based on anecdotal
evidence and the limited sample size they have experienced, but with a
large dataset we can address these questions quantitatively and
present them as clear visualisations.

@@

@@

These questions can be answered with a clear and intuitive data
visualisation of price distributions in the postcode hierarchy --- we
call this the fractal context of a property price.

\subsection{ARIMA forecasting}

Given area price histories, it's of interest to investors to speculate
on potential investment returns for a given property area. This can be
done through time series analysis using the autoregressive integrated
moving average (ARIMA) model. Investment returns can be maximised by
selecting areas with maximal growth
projections.\textsuperscript{$\star$} \\

@@

A small data science team could expand analyses, integrating novel
public and privately-acquired datasets and release them under a
rolling subscription model, aimed at private landlords and property
speculators, as well as professional real estate investment trusts
(REITs). Significant revenue could be generated through tailored
partnerships with funds and high net-worth individuals.

Should the product not succeed in a direct-to-consumer market, the
business could pivot to an analytics provider for existing letting and
sales sites, offering unique data insights indirectly to the consumer
market, or as independent fund consultants for the financial
services. Having produced a functional product positions \logo \hspace{.1em} to
succeed in innovative real estate analytics.

\begin{flushright}
{\small Full version online at: \href{http://blm.io/datarea}{blm.io/datarea}}
\end{flushright}

@@

>>>>

%% additional packages:
\usepackage{wrapfig}
\usepackage[left=1.2in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{caption}

@@

\title{ \vspace{-3em}
\includegraphics[width=5cm]{Figures/datarea.pdf} \\
{\large \#SummerDataChallenge}} % The article title

@@

I analysed the {\bf London house prices} dataset is several innovative
ways. Firstly \emph{fractal context} shows how house sales within an
arbitrary area relate to those if neighbouring districs, up and down
the postcode hierarchy. Secondly, I employed \emph{ARIMA forecasting}
to extrapolate an area's price trend with an eye to suggesting
profitable investments. Finally, these and other metrics were combined
into an \emph{investment grade} for a given postcode area. Combined
this set of analyses forms the basis of \logo, a product aimed at
``democratising real estate investment'', offering individuals and
businesses quantitative real estate insights for data-driven investment
decisions.

A full report with additional visualisations is online at {\bf
  \href{http://blm.io/datarea}{blm.io/datarea} }and scripts to
reproduce all analyses are available from {\bf
  \href{http://github.com/blmoore/summerdatachallenge}{github.com/blmoore/summerdatachallenge}}.

@@

When considering a property in a given area, you may ask a realtor
questions like: how do prices here compare to surrounding postcodes?
How have prices increased over time?  A real estate professional can
give an opinion based on their own limited sample size, but with a
large dataset we can address these questions quantitatively and
visualise the results.

@@

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.45\textwidth}
\begin{center}
\includegraphics[width=.44\textwidth]{Figures/fractal.png}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
\end{center}
\end{wrapfigure}

@@

These questions can be answered with a clear and intuitive data
visualisation of price distributions in the postcode hierarchy --- we
call this the fractal context of a property price (Figure 1).

\subsection{ARIMA modelling}

Given a time series of housing prices, it's of interest to investors
to speculate on potential investment returns for a given property
area. This can be done through time series analysis using the
autoregressive integrated moving average (ARIMA) model (Figure
2). Investment returns can be optimised by selecting areas with
maximal growth projections.\textsuperscript{$\star$} \\

@@

A small data science team will gradually expand the range of analyses
offered, integrating novel public and privately-acquired datasets and
release them under a rolling subscription model, aimed at private
landlords and property speculators, as well as professional real
estate investment trusts (REITs). Significant revenue could be
generated through tailored partnerships with funds and high net-worth
individuals.

Additionally the business could pivot to an analytics provider for
existing letting and sales sites, offering unique data insights
indirectly to the consumer market, or as independent fund consultants
for the financial services. Having produced a first-to-market
innovative product positions \logo \hspace{.1em} to succeed as a
provider of advanced real estate investment analytics. \\

@@

\vspace{1em}
\begin{flushright}
{\small An enhanced overview of this entry is available online at: \href{http://blm.io/datarea}{blm.io/datarea}}
\end{flushright}
